### 2019-07-15 manuscript/results.tex
started editing Results
Got through the "traits and diversification" section.
A lot of small wording edits, but no changes to the general presentation.

\subsection{Models}
\subsubsection{Ploidy and diversification}
When considering ploidy alone (M1. $D/P$ model), we found a larger net diversification rate for diploids than for polyploids, in agreement with \citet{mayrose_2011, mayrose_2015}.
This result holds with (\cref{figure:netdivall}A) or with the diploidization parameter (model M6 \cref{suppfigure:alldip}A) .
Incorporating a hidden state in this model, however, reduces the clear separation in diversification rate estimates between diploids and polyploids (M4. $D/P+A/B$ asym model; \cref{figure:netdivall}B, and M9 \cref{suppfigure:alldip}B).
Thus, differences in net diversification rates are explained by an unknown factor.
The lack of differences between diploid and polyploid net diversification rates is also supported by the Bayes factors shown in table \cref{table:bayesfactors} where both model M4 and the character independent model M2 have equal evidence of  being preferred over every other model of ploidy. See table \cref{supptable:M6M10} showing analogous results when diploidzation is accounted for.

\subsubsection{Breeding system and diversification}
When considering breeding system alone (M11. $I/C$ model, \cref{figure:netdivall}C), we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010}.
When a hidden state is included (M14. $I/C+A/B$ model), the large net diversification rate difference persists for hidden state $A$ but and it slightly overlaps in the  hidden state $B$ (\cref{figure:netdivall}D).
When calculating Bayes factors for all breeding system models (M11-M15) we found that the best two supported models are the models with at least asymmetric hidden states (M14 and M15 \cref{table:M11M15})
Thus, differences in net diversification rates are best explained by both breeding system and an unknown factor \citep[as in Onagraceae;][]{freyman_2019} and not only by the focal trait nor an unknown factor.
% The transition rate from SI to SC is $q_{IC}=0.3$ for both the I/C and the I/C+A/B models.

\subsubsection{Ploidy, breeding system, and diversification}
When considering ploidy and breeding system together (M16. $ID/CD/CP$ model), the net diversification rate for SI diploids was greater than for either SC diploids or SC polyploids, with or without diploidization (M16 \cref{figure:netdivall}E, M21\cref{suppfigure:alldip}E).
Thus, the difference in net diversification associated with breeding system persists even when ploidy is included in the model.
The reverse is not true, the association of ploidy with net diversification in the M1. $D/P$ model (\cref{figure:netdivall}A, \cref{suppfigure:alldip}A) appears to be driven by the subset of diploids that are SI; among SC species, net diversification rates for diploids and polyploids is not distinct.

When a hidden state is included (M19. $IC/CD/CP+A/B$ model) the net diversification rate separation amongst states ID and (CD, CP)  is clear under hidden state A, but under hidden state B the separation exist between states ID and CP, while CD overlaps with the other two states (\cref{figure:netdivall}F).
The same general pattern remains when diploidization is included (\cref{suppfigure:alldip}F), but the hidden states are reversed in the x-axis.
Bayes factors for the three state models that include the character independent model show very strong support preferring asymmetric hidden state with the focal traits models shown in  \cref{supptable:M16M20} (with diploidization \cref{supptable:M21M25}).

\subsubsection{Lumped models}
When comparing model M26. Lumped $D/P$ against M16. $ID/CD/CP$ (\cref{figure:lumped}B and C) Bayes factors reveal moderate support ($K=4.1$) preferring the three state model instead of the two state model (\cref{table:lumped}).
A similar result was obtained when comparing the lumped model for ploidy but in the presence of hidden states (model M27 \textit{vs.} M23 \cref{table:lumped}, \cref{suppfigure:lumpedDP}E and F).

We also compared lumped models for breeding system to test for the inclusion of ploidy state (M28 \cref{figure:lumped}E \textit{vs.} M16 \cref{figure:lumped}C) and we found no evidence preferring the three-state over the two state-model ($K=-0.6$, \cref{table:lumped}).
However, when accounting for hidden state,  the three-state model M18. $I/C/CD/CP+A/B$ (\cref{suppfigure:lumpedIC}F) was moderately preferred ($K=2.6$) over the lumped model M29.(\cref{suppfigure:lumpedIC}E).

>>>>

% E: I removed the model names (like, "I/C+A/B") because we don't use them in the Methods anymore.  I think it works find just to say in real words what each model includes, as it comes up, and the model numbers are good for shorthand.

\subsection{Trait-dependent diversification}

\subsubsection{Ploidy only}

When considering ploidy alone, we found a larger net diversification rate for diploids than for polyploids, in agreement with \citet{mayrose_2011, mayrose_2015}.
This result holds with (model M1, \cref{figure:netdivall}A) or without the diploidization parameter (M6, \cref{suppfigure:alldip}A).
Incorporating a hidden state in this model, however, reduces the clear separation in diversification rate estimates between diploids and polyploids (M4, \cref{figure:netdivall}B; M9, \cref{suppfigure:alldip}B).
Statistical model comparisons show a clear preference for models in which only a hidden state affects diversification or a hidden state as well as ploidy (M2 and M4; \cref{table:bayesfactors}).
Results are similar when diploidization is included (\cref{supptable:M6M10}).
Thus, the role of ploidy in net diversification is unclear, with rate differences perhaps better explained by another factor.

\subsubsection{Breeding system only}

When considering breeding system alone (M11, \cref{figure:netdivall}C), we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010}.
When a hidden state is included, the large net diversification rate difference persists for one hidden state but is diminished for the other (M14, \cref{figure:netdivall}D).
In the statistical model comparisons, the best two supported models include diversification differences due both to breeding system and to a hidden trait (M14 and M15, \cref{table:M11M15}).
Thus, breeding system seems to play a role in diversification differences, though a hidden factor does as well.

\subsubsection{Ploidy and breeding system together}

When considering ploidy and breeding system together, the net diversification rate for SI diploids was greater than for either SC diploids or SC polyploids, with or without diploidization (M16, \cref{figure:netdivall}E; M21, \cref{suppfigure:alldip}E).
Thus, the difference in net diversification associated with breeding system persists even when ploidy is included in the model.
The reverse is not true: the association of ploidy with net diversification in the simplest ploidy-only model (M1, \cref{figure:netdivall}A, \cref{suppfigure:alldip}A) appears to be driven by the subset of diploids that are SI, while among SC species, net diversification rates for diploids and polyploids are similar.

When a hidden state is included, the separation in net diversification rate of ID \vs CD and CP persists within one hidden state but is reduced in the other (M19, \cref{figure:netdivall}F).
The same general pattern remains when diploidization is included (\cref{suppfigure:alldip}F).
Model comparisons clearly favor models that include ploidy, breeding system, and the hidden trait, against the character-independent model in which the focal traits do not influence diversification (\cref{supptable:M16M20}; \cref{supptable:M21M25} with diploidization). % add model numbers

Using the lumped models, we find moderate support for obtaining a significantly better fit by adding breeding system to the ploidy-only model (M26 \vs M16, \cref{table:lumped}, \cref{figure:lumped}BC).
This is also true when a hidden trait is included (M27 \vs M23, \cref{table:lumped}, \cref{suppfigure:lumpedDP}EF).
% When comparing model M26. Lumped $D/P$ against M16. $ID/CD/CP$ (\cref{figure:lumped}B and C) Bayes factors reveal moderate support ($K=4.1$) preferring the three state model instead of the two state model (\cref{table:lumped}).
% A similar result was obtained when comparing the lumped model for ploidy but in the presence of hidden states (model M27 \textit{vs.} M23 \cref{table:lumped}, \cref{suppfigure:lumpedDP}E and F).
A similar comparison in which ploidy is added to the breeding system-only model shows no preference for the model that also includes ploidy (M28 \vs M16, \cref{table:lumped}, \cref{figure:lumped}CE).
When including a hidden state, however, the model with both focal traits is moderately preferred over the model with only breeding system (M29 \vs M18, \cref{table:lumped}, \cref{suppfigure:lumpedIC}EF).
% We also compared lumped models for breeding system to test for the inclusion of ploidy state (M28 \cref{figure:lumped}E \textit{vs.} M16 \cref{figure:lumped}C) and we found no evidence preferring the three-state over the two state-model ($K=-0.6$, \cref{table:lumped}).
% However, when accounting for hidden state,  the three-state model M18. $I/C/CD/CP+A/B$ (\cref{suppfigure:lumpedIC}F) was moderately preferred ($K=2.6$) over the lumped model M29.(\cref{suppfigure:lumpedIC}E).

From all of these types of statistical evidence, we conclude that breeding system (and a hidden factor) are strongly associated with diversification differences, and that ploidy plays a smaller role.
